My title

### 2024-11-04 paper/paper.qmd
Updated paper

# Appendix {.unnumbered}

## Appendix A: Pollster Methodology Overview and Evaluation

@@

**Population, Frame, and Sample**\
The target population for this survey consists of likely voters in Michigan.
The sampling frame is constructed to include diverse demographic groups within this population, ensuring a representative sample of voter sentiments.

@@

## Appendix B: Idealized Survey

>>>>

# Appendix {-}

# Pollster Methodology Overview and Evaluation

@@

**Population, Frame, and Sample**\
The target population is defined as the collection of all items about which we would like to speak, in this case it would be all voters in the state of Michigan.

The sampling frame defined as a list of all the items from the target population that we could get data about, in this case it would be all voters who are able to respond to the IVR or online panel survey

A sample is defined as the items from the sampling frame that we get data about, in this case that would be the 1000 people that responded to the ICR or online panel.

@@

# Idealized Survey
